% Referenser

\begin{thebibliography}{9}
	\bibitem{tsea29}
	\url{http://www.isy.liu.se/edu/kurs/TSEA29/}, information hämtad 2014-09-16.
	\bibitem{lipsmall}
	\url{http://www.commsys.isy.liu.se/sv/student/kurser/TATA62/lips}, information hämtad 2014-09-25.
	\bibitem{LIPS}
	Svensson, Tomas \& Krysander, Christian (2011), \textit{Projektmodellen LIPS}, Studentlitteratur, ISBN-9789144075259
	\bibitem{robotarm}
	\url{http://www.trossenrobotics.com/p/phantomx-ax-12-reactor-robot-arm.aspx}, information hämtad 2014-09-20.
	\bibitem{servo}
	\url{http://support.robotis.com/en/techsupport_eng.htm#product/dynamixel/ax_series/dxl_ax_actuator.htm}, information hämtad 	2014-10-24.
	\bibitem{pwmmotor}
	\url{https://docs.isy.liu.se/twiki/pub/VanHeden/DataSheets/pwm-motorstyrning.pdf}, information hämtad 2014-10-30.
	\bibitem{atmega}
	\url{http://www.atmel.com/images/doc8059.pdf}, information hämtad 2014-10-24.
	\bibitem{avstandsensor}
	\url{http://www.sharpsma.com/webfm_send/1205}, information hämtad 2014-09-24.
	\bibitem{reflexsensormodul}
	\url{https://docs.isy.liu.se/twiki/pub/VanHeden/DataSheets/reflexsensormodul.pdf}, information hämtad 2014-09-20.
	\bibitem{Muxar}
	\url{https://docs.isy.liu.se/twiki/pub/VanHeden/DataSheets/4067b.pdf}, information hämtad 2014-10-25.
	\bibitem{tristate}
	\url{https://docs.isy.liu.se/twiki/pub/VanHeden/DataSheets/sn74ls125.pdf}, information hämtad 2014-11-10.
	\bibitem{levelshifters}
	\url{http://www.ti.com/lit/ds/symlink/txb0104.pdf}, information hämtad 2014-11-01.
	\bibitem{spi}
	\url{http://en.wikipedia.org/wiki/Serial_Peripheral_Interface_Bus}, information hämtad 2014-10-24.
\end{thebibliography}
